Refactoring the \texttt{nls()} function in R

### 2022-06-21 RefactoringNLS/RefactoringNLS.Rmd
minor edits, acknowledge Gillespie

Such goals align with the aims of **unit testing** 
(e.g., https://towardsdatascience.com/unit-testing-in-r-68ab9cc8d211), as well
as with R package checking tools ?? reference??. ??Other refs.

@@

<!-- ?? Arkajyoti -- do you want to expand? -->
<!-- Trying to trim a lot of words, so am makign reference to package. Is it ready -->
<!-- for others to use? -->

@@

<!-- - VarietyInNonlinearLeastSquaresCodes.Rmd: a review of the different algorithms and -->
<!--   the many choices in their implementation for nonlinear least squares. This is still -->
<!--   a DRAFT at 2021-8-20. ?? fix -->

<!-- ?? Arkajyoti: I think TestsDoc is too preliminary to mention, though the links might be -->
<!-- useful. Perhaps incorporate in the nlsCompare repo. -->
<!-- - TestsDoc.Rmd (??citation) is a survey of testing tools in R. It has more  -->
<!--   general possibilities  -->
<!--   and fits into the subject of regression testing, in which case a  -->
<!--   more extensive literature review will be needed.  Note that this -->
<!--   document reflects the work in the the "Problem sets and test infrastructure" -->
<!--   below. -->

@@

<!-- ?? needs more focus of where it may appear. -->
<!-- - DerivsNLS.Rmd ??citation: a document to explain different ways in which Jacobian information -->
<!--   is supplied to nonlinear least squares computation in R. File `ExDerivs.R` is -->
<!--   a DRAFT of a script to provide examples. -->

>>>>

Such goals align with the aims of **unit testing** 
(e.g., https://towardsdatascience.com/unit-testing-in-r-68ab9cc8d211, @HWtestthat11, @HWdevtools21
and the conventional R package testing tools).

@@

<!-- Arkajyoti -- do you want to expand? -->
<!-- No. I think it would be tangential to the goal of the paper. We can have a -->
<!-- separate article for that, maybe? -->
<!-- Trying to trim a lot of words, so am making reference to package. Is it ready -->
<!-- for others to use? -->

@@

<!-- - VarietyInNonlinearLeastSquaresCodes.Rmd: a review of the different algorithms and -->
<!--   the many choices in their implementation for nonlinear least squares. This is still -->
<!--   a DRAFT at 2022-6-20. -->

<!-- Response to query about TestsDoc -->
<!-- 4. Testing infrastructure, I think, is a general topic and not -->
<!-- particularly relevant to nls(); i.e., it is important for all packages. -->
<!-- So, I don't think we need to include that in RefactoringNLS. Could be a -->
<!-- separate blog maybe?   -->

<!-- Arkajyoti: I think TestsDoc is too preliminary to mention, though the links might be -->
<!-- useful. Perhaps incorporate in the nlsCompare repo. -->
<!-- - TestsDoc.Rmd (?citation) is a survey of testing tools in R. It has more  -->
<!--   general possibilities  -->
<!--   and fits into the subject of regression testing, in which case a  -->
<!--   more extensive literature review will be needed.  Note that this -->
<!--   document reflects the work in the the "Problem sets and test infrastructure" -->
<!--   below. -->

@@

<!-- This needs more focus of where it may appear. I'm thinking of a blog post -- JN-->
<!-- - DerivsNLS.Rmd ?citation: a document to explain different ways in which Jacobian information -->
<!--   is supplied to nonlinear least squares computation in R. File `ExDerivs.R` is -->
<!--   a DRAFT of a script to provide examples. -->

### 2022-06-21 RefactoringNLS/RefactoringNLS.tex
minor edits, acknowledge Gillespie

\begin{verbatim}
## nlsr object: x 
## residual sumsquares =  9.4726  on  12 observations
##     after  16    Jacobian and  17 function evaluations
##   name            coeff          SE       tstat      pval      gradient    JSingval   
## b1                     2U           NA         NA         NA           0       23.35  
## b2               4.43325            NA         NA         NA   1.015e-10           0  
## b3                     3U           NA         NA         NA           0           0
\end{verbatim}

@@

Such goals align with the aims of \textbf{unit testing} (e.g.,
\url{https://towardsdatascience.com/unit-testing-in-r-68ab9cc8d211}), as
well as with R package checking tools ?? reference??. ??Other refs.

@@

>>>>

\begin{verbatim}
## nlsr object: x 
## residual sumsquares =  9.4726  on  12 observations
##     after  16    Jacobian and  17 function evaluations
##   name            coeff          SE       tstat      pval      gradient    JSingval   
## b1                     2U           NA         NA         NA           0       23.35  
## b2               4.43325            NA         NA         NA   1.583e-10           0  
## b3                     3U           NA         NA         NA           0           0
\end{verbatim}

@@

Such goals align with the aims of \textbf{unit testing} (e.g.,
\url{https://towardsdatascience.com/unit-testing-in-r-68ab9cc8d211},
Wickham (\protect\hyperlink{ref-HWtestthat11}{2011}), Wickham et al.
(\protect\hyperlink{ref-HWdevtools21}{2021}) and the conventional R
package testing tools).

@@

\leavevmode\vadjust pre{\hypertarget{ref-HWtestthat11}{}}%
Wickham, Hadley. 2011. {``Testthat: Get Started with Testing.''}
\emph{The R Journal} 3: 5--10.
\url{https://journal.r-project.org/archive/2011-1/RJournal_2011-1_Wickham.pdf}.

\leavevmode\vadjust pre{\hypertarget{ref-HWdevtools21}{}}%
Wickham, Hadley, Jim Hester, Winston Chang, and Jennifer Bryan. 2021.
\emph{Devtools: Tools to Make Developing r Packages Easier}.
\url{https://CRAN.R-project.org/package=devtools}.
